Output Summary

### 2023-05-30 03-post-process/compare-sim-to-obs.Rmd
Remove references to sea lion survival
No longer part of model. Was discovered to be causing problems for ocean survival estimates (the stair-step mixed with a time-constant ocean survival was not working well)
Fix bug with identifying which years are simulated

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output:
   html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 0.5
    input: numeric
editor_options: 
  chunk_output_type: console
---

@@

```{r select-years}
# all of the years included in the model
all_yrs = as.numeric(rownames(jags_data$phi_SL))

>>>>

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output:
   html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong_sim"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 0.5
    input: numeric
editor_options: 
  chunk_output_type: console
---

@@

```{r select-years}
# the years included in the model
all_yrs = as.numeric(dimnames(jags_data$Mb_obs)[[1]])

### 2023-05-30 03-post-process/output-plots.Rmd
Remove references to sea lion survival
No longer part of model. Was discovered to be causing problems for ocean survival estimates (the stair-step mixed with a time-constant ocean survival was not working well)
Fix bug with identifying which years are simulated

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "test-rmd_vshort"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_egg_to_parr_surv:
    label: "Include Egg-to-Parr Survival Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_process_model:
    label: "Include Misc. Process Model Output?"
    value: TRUE
  include_equiv_rates:
    label: "Include Equivilency Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_noise_term_diags:
    label: "Include Noise Term Diagnostic Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
editor_options: 
  chunk_output_type: console
---

@@

```{r dimension-ids}
# the years included by the model
all_yrs = as.numeric(dimnames(jags_data$phi_SL)[[1]])

>>>>

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_egg_to_parr_surv:
    label: "Include Egg-to-Parr Survival Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_process_model:
    label: "Include Misc. Process Model Output?"
    value: TRUE
  include_equiv_rates:
    label: "Include Equivilency Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_noise_term_diags:
    label: "Include Noise Term Diagnostic Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
editor_options: 
  chunk_output_type: console
---

@@

```{r dimension-ids}
# the years included in the model
all_yrs = as.numeric(dimnames(jags_data$Mb_obs)[[1]])
